Climate change projected to reduce European life expectancy

### 2018-03-31 MS-cclifeexpec.Rmd
Update MS-cclifeexpec.Rmd

```{r setup, include=FALSE, cache =TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(png)
rm(list=ls())
library(tidyverse)
library(HMDHFDplus)
library(tmap)
library(tmaptools)
library(RColorBrewer)
library(data.table)

@@

myusername <- "hauer@uga.edu"
mypassword <- "fuckhead"

>>>>

```{r setup, include=FALSE, cache =TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(png)
rm(list=ls())
library(tidyverse)
library(HMDHFDplus)
library(tmap)
library(tmaptools)
library(RColorBrewer)
library(data.table)
library(getPass)

@@

myusername <- getPass()
mypassword <- getPass()
